\documentclass[11pt,
a4paper,
parskip=half, % This is some extra vertical space between paragraphs, the suggestion is 2cm which is really ugly, so we use what koma script gives us
% you can also set it to full for even more space. But there is a bad tex style decision: parskip also changes the spacing between listitems such as
% enumerate and itemize. For this purpose we include the enumitem package and set itemsep=.5em, of course you can change this
BCOR=10mm, % BCOR is binding correction
ngerman, english
% if you'd rather have a one sided thesis, add `oneside' to the documentclass
% oneside,
% ngerman is needed for hyphenation if the thesis contains parts written in German, switch order with english if you write mainly in English.
% Remember to change order in the babel package (below) as well.
% Last language is the preferred one.
]{scrbook}
\usepackage[english]{babel} % If you write mainly in English change order to ngerman, english. Also change that in the documentclass options above.
% Include of titling must happen before \title etc.
% that's why it's not in setup.tex
\usepackage{titling}
\input{chapters/0_preamble.tex}

\begin{document}
	\setlength{\abovedisplayskip}{0.25cm}
	\setlength{\belowdisplayskip}{0.25cm}
	\setlength{\abovedisplayshortskip}{0.25cm}
	\setlength{\belowdisplayshortskip}{0.25cm}
	 \raggedbottom
\newcommand{\HorizontalLine}{\rule{\textwidth}{0.4mm}}

\input{chapters/0_0-titlepage_en.tex}
\pagebreak

\frontmatter
\input{chapters/0_1-declaration.tex}
\pagebreak

\input{chapters/0_2-abstract.tex}

\chapter{Acknowledgements}
Firstly, I would like to truly give my thanks to my advisers Daniel and Tanja. I was blessed to have two of the most ingenious researches helping and advising me along this journey. Daniel showing me the way of trace abstraction, since 2016, teaching me how to use and program on Ultimate, while Tanja showed me how to use mathematics and logic, not only in this project but many before. I am endlessly grateful for their guidance, expertise, and support. Thank you so much. \par 
I want to thank my family for their endless, unwavering support. Without my mother, father, sister, and grandparents I would not have been able to make this journey. \par 
Next, I would like to give gratitude to my friends. Firstly, my dearest friend Dennis, who was always there for me, being online or offline. You are my brother, thank you, for the good times while I was struggling. I want to thank Gabri, the best jazz singer and model in the world. Thank you for showing me a world beyond computers, mathematics and logic. My friends Phil and Vinz, who, after three years, still owe me an Dinghy. My old and dear friends, Johnny, Matze, Domi, Quini, Quoci, Achim, and Sebi. Thank you all, for enduring my everlasting madness. Jake, the best DJ Freiburg has ever seen, our conversations in the bar, frequented by SC players, were legendary. Mimi thank you for the good times we had drinking soup which some people call lecker lecker. Edgar, Philippe Bieli aus dem Kanton Aargau, Mazear, and Barsch thank you for spending time with me.

\tableofcontents
\pagebreak

\mainmatter
\chapter{Introduction}
\label{intro}
\input{chapters/1_introduction.tex}

\chapter{Related Work}
\label{relWork}
\input{chapters/x_relatedWork.tex}
\pagebreak

\chapter{Preliminaries}
\label{background}
\input{chapters/2_background.tex}

\chapter{Loop Summarization using \qvasr}
\label{qvasr}
\input{chapters/4_qvasr.tex}

\begin{comment}
	\section{Extension to \qvasrs}
	\label{qvasrs}
	\input{chapters/5_qvasrs.tex}
\end{comment}

\chapter{Trace Abstraction with \qvasr}
A loop in a program can potentially introduce infinitely many program traces that the trace abstraction scheme has to prove infeasible. In this chapter we will introduce methods of utilizing \qvasr-based loop summarization to minimize the number of traces created by loops. We present two approaches, firstly an implementation of the \textsl{abstract} step of trace abstraction as seen in Figure \ref{traceAbstractionScheme} utilizing loop summaries directly in traces, secondly a way of transforming a given program's control-flow graph to replace loops entirely by loop summaries.
\label{qvasrAbstracion}
\section{Accelerated Interpolation}
\input{chapters/3_accelerated_interpolation.tex}
\label{accelInterpol}

\section{Control-Flow Graph Transformation}
\input{chapters/6_implementation.tex}
\label{icfgTransformation}

\chapter{Evaluation}
\label{eval}
\input{chapters/7_evaluation.tex}

\chapter{Future Work}
\label{futrWork}
\input{chapters/8_outlook.tex}

	\setlength{\abovedisplayskip}{0.25cm}
\setlength{\belowdisplayskip}{0.25cm}
\setlength{\abovedisplayshortskip}{0.25cm}
\setlength{\belowdisplayshortskip}{0.25cm}
\chapter{Conclusion}
\label{concl}
\input{chapters/9_conclusion.tex}


\pagebreak
\bibliographystyle{ieeetr}
\bibliography{bib/bib}

\listoffigures

\end{document}